Documentation of Scripts for Generating Random MISDP Instances

### 2020-09-09 RIP-MISDP-Paper/scripts/RandomInstancesMISDP.tex
Correct cbf-generation of RIP instances

    &\text{F}\quad{\color{blue} (L+)}  &\tfrac{1}{2}n(n+1) \qquad & X_{ij},\;

@@

\# cons: $n(n+1)+n+2 \quad {\color{blue}(\tfrac{1}{2}n(n+1)+n+2)}$, \qquad

@@

    &\text{L-} &\tfrac{1}{2}n(n+1) \qquad & {\color{blue}-z_i - X_{ij} \leq 0},\quad & 0
    \leq j \leq i \leq n-1 &\qquad {\color{blue} \text{(this line is cancelled)}}\\
    &\text{L+} &\tfrac{1}{2}n(n+1) \qquad & z_i - X_{ij} \geq 0,\quad & 0

@@

\# entries: $2n(n+1)+3n \quad {\color{blue} (- n(n+1))}$ \\
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n+1)$ constraints are cancelled, so
  that $\tfrac{1}{2}n(n+1)$ needs to be subtracted from the first column

@@

    & n+\tfrac{1}{2}i(i+1)+j \quad & i \quad & -1.0\; (i = j),\,

@@

    \quad & 0 \leq j \leq i \leq n-1\\
    & n+\tfrac{1}{2}i(i+1)+j \quad & n+\tfrac{1}{2}i(i+1)+j \quad & -1.0
    \quad & {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq j \leq i \leq n-1 \\
    & n+\tfrac{1}{2}n(n+1)+\tfrac{1}{2}i(i+1)+j \quad & i \quad & 1.0\; (i

@@

    & n+\tfrac{1}{2}n(n+1)+\tfrac{1}{2}i(i+1)+j \quad &

@@

    0 \leq j \leq i \leq n-1 \\
    & n+n(n+1) \quad & n+\tfrac{1}{2}i(i+1)+i \quad & 1.0 \quad & \tr(X) -

@@

    & n+n(n+1)+1 \quad & i \quad & 1.0 \quad & \sum z_i - k \geq 0 \quad &

@@

{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n+1)$ constraints are cancelled, so
  that $\tfrac{1}{2}n(n+1)$ needs to be subtracted from the first column

@@

    & i \quad & -1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    & n+n(n+1) \quad & 1.0 \quad & \tr(X) - 1 = 0 \quad & i = 0,\dots,n-1

@@

    & n+n(n+1)+1 \quad & 1.0 \quad & \sum z_i - k \geq 0 \quad & i =

@@

\# cons: $n(n+1)+n+2 \quad {\color{red}(+\tfrac{1}{2}n(n+3)(n+2))}$, \qquad

@@

    &\text{L-} &\tfrac{1}{2}n(n+1) \qquad & -z_i - X_{ij} \leq 0,\;
    {\color{blue} (-X_{ij} \leq 0)}\quad & 0
    &\text{L+} &\tfrac{1}{2}n(n+1) \qquad & z_i - X_{ij} \geq 0,\quad & 0

@@

\# entries: $n(n+1)+n$ \quad {\color{red} $+
  n\cdot(3n+5+\tfrac{1}{2}n(n+1))$ }\\

@@

    &n+\tfrac{1}{2}i(i+1)+j \quad & 0 \quad & i \quad & j \quad & -1.0\,
    (i\neq j),\; -\tfrac{1}{2}\, (i=j) \quad & -z_j - X_{ij} \leq 0 \quad &
    0 \leq j \leq i \leq n-1 \\
    &n+\tfrac{1}{2}n(n+1)+\tfrac{1}{2}i(i+1)+j \quad & 0 \quad & i \quad &
    j \quad & -1.0\, (i\neq j),\; -\tfrac{1}{2}\, (i=j) \quad & +z_j -
    X_{ij} \geq 0 \quad & 0 \leq j \leq i \leq n-1 \\
    &n+n(n+1)\quad & 0 \quad & i \quad & i \quad & 1.0 \quad & \tr(X) - 1

@@

\textbf{ACOORD} (scalar cons $i$ | scalar var $j$ val) \\
\# entries: $n(n+1)+2n$ \qquad {\color{red} $(+2n)$} \qquad {\color{blue}
  $-(\tfrac{1}{2}n(n+1))$} \\

@@

    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + n+1} \quad & {\color{red}i} \quad &
    {\color{red}-\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle - \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + 2n+2} \quad & {\color{red}i} \quad &
    {\color{red}\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle + \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\

@@

    &i \quad & i \quad & -1.0 \quad & -z_i + 1 = 0 \quad & i = 0,\dots,n-1
    &n+\tfrac{1}{2}i(i+1)+j \quad & i \quad & -1.0\, (i =
    j),\; {\color{orange} -\tfrac{1}{2},\,(i \neq j)} \quad & {\color{blue}-z_i - X_{ij}
    \leq 0} \quad & 0 \leq j \leq i \leq n-1 \quad {\color{blue}
    (\text{this line is cancelled})} \\
    &n+\tfrac{1}{2}n(n+1)+\tfrac{1}{2}i(i+1)+j \quad & i \quad & 1.0\, (i =
    j),\; {\color{orange} \tfrac{1}{2},\,(i \neq j)}\quad & z_i - X_{ij}
    \geq 0 \quad & 0 \leq j \leq i \leq n-1 \\
    &in+n(n+1)+1 \quad & i \quad & 1.0 \quad & \sum z_i - k \leq 0 \quad &
    i = 0,\dots,n-1 \\
\# entries: $n+2 \qquad {\color{red} (+n(n+1))}$ \\
  &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + j} \quad & {\color{red}-1.0}
  \quad & {\color{red} \langle P_i, E_{j+1,j+1} \rangle - 1 = 0} \quad & {\color{red} j
  = 0,\dots,n,\; i = 0,\dots,n-1} \\
    &i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    &n(n+1)+n \quad & -1.0 \quad & \tr(X) -1 = 0 \quad & \\
    &n(n+1)+n+1 \quad & k \quad & \sum z_i - k \leq 0 \quad & \\

@@

>>>>

    &\text{F}\quad{\color{blue} (\text{L}+)}  &\tfrac{1}{2}n(n+1) \qquad & X_{ij},\;

@@

\# cons: $2n^2+n+2 \quad {\color{blue}(n^2+n+2)}$, \qquad

@@

    &\text{L-} &n^2 \qquad & {\color{blue}-z_i - X_{ij} \leq 0},\quad & 0
    \leq i,\, j \leq n-1 &\qquad {\color{blue} \text{(this line is cancelled)}}\\
    &\text{L+} &n^2 \qquad & z_i - X_{ij} \geq 0,\quad & 0
    \leq i, \, j \leq n-1 \\

@@

\# entries: $4n^2+3n \quad {\color{blue} (- 2n^2)}$ \\
{\color{blue} If strgbnds = 1, then $n^2$ constraints are cancelled, so
  that $n^2$ needs to be subtracted from the first column

@@

    & n+in+j \quad & i \quad & -1.0\; (i = j),\,

@@

    \quad & 0 \leq i,\, j \leq n-1\\
    & n+in+j \quad & n+\tfrac{1}{2}i(i+1)+j \quad & -1.0
    \quad & {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq i,\, j \leq
    n-1, \; i \geq j \\
    & n+in+j \quad & n+\tfrac{1}{2}j(j+1)+i \quad & -1.0
    \quad & {\color{blue}-z_j - X_{ij} \leq 0} \quad & 0 \leq i,\, j \leq
    n-1, \; i < j \\
    & n+n^2+in+j \quad & i \quad & 1.0\; (i

@@

    \leq i,\, j \leq n-1 \\
    & n+n^2+in+j \quad &

@@

    0 \leq i,\, j \leq n-1,\; i \geq j \\
    & n+n^2+in+j \quad &
    n+\tfrac{1}{2}j(j+1)+i \quad & -1.0 \quad & z_j - X_{ij} \geq 0 \quad &
    0 \leq i,\, j \leq n-1,\; i < j \\
    & n+2n^2 \quad & n+\tfrac{1}{2}i(i+1)+i \quad & 1.0 \quad & \tr(X) -

@@

    & n+2n^2+1 \quad & i \quad & 1.0 \quad & \sum z_i - k \geq 0 \quad &

@@

{\color{blue} If strgbnds = 1, then $n^2$ constraints are cancelled, so
  that $n^2$ needs to be subtracted from the first column

@@

    & i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    & n+2n^2 \quad & -1.0 \quad & \tr(X) - 1 = 0 \quad & i = 0,\dots,n-1

@@

    & n+2n^2+1 \quad & -k  \quad & \sum z_i - k \geq 0 \quad & i =

@@

\# cons: $2n^2+n+2 \quad {\color{red}(+\tfrac{1}{2}n(n+3)(n+2))} \quad
{\color{blue} (-\tfrac{1}{2}n(n-1))}$, \qquad

@@

    &\text{L-} &n^2\quad {\color{blue}(\tfrac{1}{2}n(n+1))} \qquad & -z_i - X_{ij} \leq 0,\;
    {\color{blue} (-X_{ij} \leq 0)}\quad & 0 \leq i,\, j \leq n-1\quad {\color{blue}(0
    \leq j \leq i \leq n-1)} \\
    &\text{L+} &n^2 \qquad & z_i - X_{ij} \geq 0,\quad & 0

@@

\# entries: $2n^2+n$ \quad {\color{red} $+
  n\cdot(3n+5+\tfrac{1}{2}n(n+1))$ } \quad {\color{blue} $- \tfrac{1}{2}n(n-1)$}\\

@@

    &n+in+j \quad & 0 \quad & i \quad & j \quad & -1.0\,
    (i = j),\; -\tfrac{1}{2}\, (i\neq j) \quad & -z_j - X_{ij} \leq 0 \quad &
    0 \leq i,\, j \leq n-1,\; i \geq j \\
    &n+in+j \quad & 0 \quad & j \quad & i \quad & -1.0\,
    (i = j),\; -\tfrac{1}{2}\, (i\neq j) \quad & -z_j - X_{ij} \leq 0 \quad &
    0 \leq i,\, j \leq n-1,\; i < j \\
    &n+n^2+in+j \quad & 0 \quad & i \quad &
    j \quad & -1.0\, (i = j),\; -\tfrac{1}{2}\, (i\neq j) \quad & +z_j -
    X_{ij} \geq 0 \quad & 0 \leq i,\, j \leq n-1,\; i \geq j \\
    &n+n^2+in+j \quad & 0 \quad & j \quad &
    i \quad & -1.0\, (i = j),\; -\tfrac{1}{2}\, (i\neq j) \quad & +z_j -
    X_{ij} \geq 0 \quad & 0 \leq i,\, j \leq n-1,\; i < j \\
    &n+2n^2 \quad & 0 \quad & i \quad & i \quad & 1.0 \quad & \tr(X) - 1

@@

{\color{blue} If strgbnds = 1, then the first two lines are replaced by the
  following line:

@@

    n+\tfrac{1}{2}i(i+1)+j \quad  0 \quad i \quad  j \quad  -1.0
    \quad - X_{ij} \leq 0 \quad 0 \leq j \leq i \leq n-1,

@@

  so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the first column
  (scalar cons $i$) in the third to fifth line.\\

@@

\noindent
\textbf{ACOORD} (scalar cons $i$ | scalar var $j$ val) \\
\# entries: $2n^2+2n$ \qquad {\color{red} $(+2n)$} \qquad {\color{blue}
  $(-n^2)$} \\
\[
  \begin{aligned}
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + n+1} \quad & {\color{red}i} \quad &
    {\color{red}-\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle - \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
    &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + 2n+2} \quad & {\color{red}i} \quad &
    {\color{red}\tfrac{1}{2}} \quad & {\color{red} \langle P_i, E_{00}
      \rangle - \tfrac{1}{2}\langle X,E_{ii}\rangle + \tfrac{1}{2}z_i = 0}
    \quad &{\color{red} i = 0,\dots,n-1} \\
  \end{aligned}
\]
{\color{red} If the valid SOCP-inequality is added, then $\tfrac{1}{2}n(n+3)(n+2)$ needs
  to be added to the entries in the first column (scalar cons $i$).}
\[
  \begin{aligned}
    &i \quad & i \quad & -1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0, \dots,
    n-1 \\
    &n+in+j \quad & i \quad & -1.0\, (i =
    j),\; {\color{orange} -\tfrac{1}{2},\,(i \neq j)} \quad & {\color{blue}-z_i - X_{ij}
    \leq 0} \quad & 0 \leq i,\, j \leq n-1 \quad {\color{blue}
    (\text{this line is cancelled})} \\
    &n+n^2+in+j \quad & i \quad & 1.0\, (i =
    j),\; {\color{orange} \tfrac{1}{2},\,(i \neq j)}\quad & z_i - X_{ij}
    \geq 0 \quad & 0 \leq i,\, j \leq n-1 \\
    &n+2n^2+1 \quad & i \quad & 1.0 \quad & \sum z_i - k \leq 0 \quad &
    i = 0,\dots,n-1 \\
  \end{aligned}
\]
\noindent
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n-1)$ constraints are
  cancelled, so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the
  first column (scalar cons $i$) in the third and fourth line.\\
}

\textbf{BCOORD} (scalar cons $i$ | val) \\
\# entries: $n+2 \qquad {\color{red} (+n(n+1))}$ \\
\[
\begin{aligned}
  &{\color{red}i\cdot\tfrac{1}{2}(n+3)(n+2) + j} \quad & {\color{red}-1.0}
  \quad & {\color{red} \langle P_i, E_{j+1,j+1} \rangle - 1 = 0} \quad & {\color{red} j
  = 0,\dots,n,\; i = 0,\dots,n-1} \\
  \end{aligned}
\]
{\color{red} If the valid SOCP-inequality is added, then $\tfrac{1}{2}n(n+3)(n+2)$ needs
  to be added to the entries in the first column (scalar cons $i$).}
\[
  \begin{aligned}
    &i \quad & 1.0 \quad & -z_i + 1 \geq 0 \quad & i = 0,\dots,n-1 \\
    &2n^2+n \quad & -1.0 \quad & \tr(X) -1 = 0 \quad & \\
    &2n^2+n+1 \quad & k \quad & \sum z_i - k \leq 0 \quad & \\
  \end{aligned}
\]
\noindent
{\color{blue} If strgbnds = 1, then $\tfrac{1}{2}n(n-1)$ constraints are
  cancelled, so that $\tfrac{1}{2}n(n-1)$ needs to be subtracted from the
  first column (scalar cons $i$) in the second and third line.\\
}
}
